### 2020-09-15 proposals/doe-proposal/proposal-narrative.tex
spacing on proposals reduced

{\centering 
    \textbf{Title\\
    Call \\
    }
    Name (PI) - Affiliation\\
    Name (co-PI) - Affiliation 
\par
}
\vspace{\baselineskip}

@@

%\begin{wrapfigure}{l}{0.32\textwidth}
%    \includegraphics[width=0.30\textwidth]{}
%    \captionsetup{justification=centering}
%    \caption{WSC simulator.}
%    \label{fig-wsc-simulator}
%\end{wrapfigure}
\noindent 
\\
\noindent\textbf{Motivation.} \textit{Context.}

\noindent\textbf{Overall Objective.} The overall objective of this project is to 
\\

@@

\vspace{\baselineskip}

@@

\textit{Unique project features.} 
\\

\noindent\textbf{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project. Many of the Tasks overlap. Research will be concurrent and mutually dependent across the investigators.
\\

\noindent\textbf{Workscope 1. Task I. Title.} (\textit{Lead - ; Support - }) 
\\

@@

@@

\vspace{\baselineskip}

\noindent\textbf{Contribution to Advancing State of the Art in Nuclear Engineering and .} 
\\

\noindent\textbf{Description of Facilities to be Utilized to Execute Scope.} 
\\

\noindent\textbf{Challenges to Accomplish Tasks and Planned Mitigations.} 
\\

@@

\vspace{\baselineskip}

\noindent\textbf{Information, Data, and Plans.} All information has been presented in the technical scope.\\

\noindent\textbf{Quality Assurance.} Our project team have practiced a QA approach, consistent with the graded approach established by the DOE Technical Integration Office, per the NEUP website and any additional requirements deemed necessary during contracting. All projects undergo safety review by experts. We have followed this QA expectation in all ongoing awards.\\

\noindent\textbf{Mandatory Requirements.} We abide by current and pending information on nuclear-related federal funding contained in Form 3204. The Mandatory, Go/No-go, requirements will be coordinated with the institutional Office of Sponsored Research, the general counsel, and the Office of Technology Transfer. Each PI noted below will assume responsibility as the point of contact.\\

>>>>

{\centering 
    \textbf{Title\\
    Call \\
    }
    Name (PI) - Affiliation\\
    Name (co-PI) - Affiliation 
\par
}

\vspace{0.5\baselineskip}

@@

%\begin{wrapfigure}{l}{0.32\textwidth}
%    \includegraphics[width=0.30\textwidth]{}
%    \captionsetup{justification=centering}
%    \caption{WSC simulator.}
%    \label{fig-wsc-simulator}
%\end{wrapfigure}
\noindent

\vspace{0.5\baselineskip}

\noindent\textbf{Motivation.} \textit{Context.}

\vspace{0.5\baselineskip}

\noindent\textbf{Overall Objective.} The overall objective of this project is to

\vspace{0.5\baselineskip}

@@

\vspace{0.5\baselineskip}

@@

\textit{Unique project features.}

\vspace{0.5\baselineskip}

\noindent\textbf{Logical Path, Work Scope, Description of Tasks.} The Logical Path and the proposed Work Scope is described below in terms of the defined Tasks for the project. Many of the Tasks overlap. Research will be concurrent and mutually dependent across the investigators.

\vspace{0.25\baselineskip}

\noindent\textbf{Workscope 1. Task I. Title.} (\textit{Lead - ; Support - })

\vspace{0.25\baselineskip}

@@

\vspace{0.5\baselineskip}

@@

\vspace{\baselineskip}
\vspace{0.5\baselineskip}

\noindent\textbf{Contribution to Advancing State of the Art in Nuclear Engineering and .}

\vspace{0.5\baselineskip}

\noindent\textbf{Description of Facilities to be Utilized to Execute Scope.}

\vspace{0.5\baselineskip}

\noindent\textbf{Challenges to Accomplish Tasks and Planned Mitigations.}

\vspace{0.5\baselineskip}

@@

\vspace{0.5\baselineskip}

\noindent\textbf{Information, Data, and Plans.} All information has been presented in the technical scope.

\vspace{0.5\baselineskip}

\noindent\textbf{Quality Assurance.} Our project team have practiced a QA approach, consistent with the graded approach established by the DOE Technical Integration Office, per the NEUP website and any additional requirements deemed necessary during contracting. All projects undergo safety review by experts. We have followed this QA expectation in all ongoing awards.

\vspace{0.5\baselineskip}

\noindent\textbf{Mandatory Requirements.} We abide by current and pending information on nuclear-related federal funding contained in Form 3204. The Mandatory, Go/No-go, requirements will be coordinated with the institutional Office of Sponsored Research, the general counsel, and the Office of Technology Transfer. Each PI noted below will assume responsibility as the point of contact.

\vspace{0.5\baselineskip}
